### 2019-09-20 reports/thesis/chapters/5_inference.tex
Revise

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{X-ray image}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\texttt{aRTist} simulation}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{A projection of the test sample, from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} simulated projection to detect purposefully manufactured voids. The $p$-values obtained were used for hypotheses testing. Pixels detected as positive are shown in red in d) using the \cite{benjamini1995controlling} procedure at the 5\% false discovery rate level.}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{Image with positive pixels}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}

>>>>

\begin{figure}
  \centering
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_scan.eps}
      \caption{Obtained projection (\SI{}{\adu})}
      \label{fig:inference_inferenceIntro_inference_scan}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_artist.eps}
      \caption{\emph{aRTist} projection (\SI{}{\adu})}
      \label{fig:inference_inferenceIntro_inference_artist}
    \end{subfigure}
  }
  \centerline{
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_logp.eps}
      \caption{$-\log p\text{-values}$}
      \label{fig:inference_inferenceIntro_inference_pvalue}
    \end{subfigure}
    \begin{subfigure}[b]{\subSize}
      \includegraphics[width=\textwidth]{../figures/inference/inferenceIntro_positivePixels.eps}
      \caption{Positive pixels overlaid on a)}
      \label{fig:inference_inferenceIntro_inference_positivePixels}
    \end{subfigure}
  }
  \caption{The obtained projection of the test sample (a), from the \texttt{AbsFilter} at \ang{120} dataset, was compared to the \emph{aRTist} projection (b) to detect purposefully manufactured voids. The $p$-values (c) obtained were used for hypotheses testing. Pixels detected as positive are shown in red in d) using the \cite{benjamini1995controlling} procedure at the 5\% false discovery rate level.}
  \label{fig:inference_inferenceIntro_inference}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_sig.eps}
        \caption{Obtained projection (\SI{}{\adu})}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius1}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. b) $p$-values on the log scale. c) and d) Empirical null mean and deviation.}
  \label{fig:inference_AbsFilterDeg120_inference_radius4}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg120_radius4.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg120_inference_radius4}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.05\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{AbsFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiAbsFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiAbsFilterDeg30_inference_radius1}
\end{figure}

@@

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{30} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg30_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg30_inference}
\end{figure}

\begin{figure}[p]
  \centering
    \centerline{
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=1.03\textwidth, height=5.6cm]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_sig.eps}
        \caption{{Obtained projection (\SI{}{\adu})}}
      \end{subfigure}
      \begin{subfigure}[b]{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_logp.eps}\vspace{-1mm}
        \caption{$-\log p$}
      \end{subfigure}
    }
    \centerline{
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullMean.eps}
        \caption{Empirical null mean}
      \end{subfigure}
      \begin{subfigure}{\subSize}
        \includegraphics[width=\textwidth]{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1_nullStd.eps}
        \caption{Empirical null std}
      \end{subfigure}
    }
  \caption{Resulting inference when using the empirical null filter on the \texttt{TiFilter} at \ang{120} projection and on each segment independently. A kernel radius of $r=\addNumber{../figures/inference/DefectDetectSubRoiTiFilterDeg120_radius1.txt}\,\SI{}{\pixel}$ was used. a) Highlighted in red are positive pixels at the 5\% FDR level. The test statistics from all segments were combined in the BH procedure. b) $p$-values on the log scale. c) and d) Empirical null mean and standard deviation.}
  \label{fig:inference_subroiTiFilterDeg120_inference}
\end{figure}
